### 2021-10-21 paper/pldi22/formal.tex
More formalization in appendix

\section{$\ires$ Specialization}\label{sec:formal}

We first define $\ires$ with its abstract syntax, states, and concrete
semantics.  Then, we define syntactic views as JavaScript ASTs with abstract
nodes. Finally, we define the specialization of $\ires$ as a transformation to
specialize $\ires$ functions.  To prove the semantics preservation of the
specialization, we introduce an observational semantics of $\ires$ and prove
that each specialized $\ires$ functions has equivalent observational semantics
of the corresponding original one.

@@

First, we define abstract syntax, states, and concrete semantics of $\ires$.

@@

States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
$\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
\addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
a triple of a label, a environment, and an optional calling context $\ctxtopt
\in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
\envset$ is a finite mapping from variables to values. A value $\val \in
\valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
\in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
\treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
finite mappings from strings to values.

@@

\subsection{Specialization}

@@

\subsubsection{Constant Propagation Transformation}

@@

\subsubsection{Cleanup Transformation}

@@

\subsection{Observational Semantics}

@@

\section{Syntatic Views}

@@

>>>>

\section{JavaScript Semantics Specialization with Syntactic Views}\label{sec:formal}

We first define $\ires$ as a specification language to describe JavaScript
semantics.  Then, we define a function specialization in $\ires$ with two
different source-to-source transformations: a constant propagation
transformation and a redundancy elimination transformation.  We prove the
semantics preservation of function specialization under an observational
semantics.  Finally, we define the JavaScript semantics specialization with
syntactic views using function specialization.

@@

We first introduce $\ires$, an \textbf{I}ntermediate \textbf{R}epresentations
for \textbf{E}CMA\textbf{S}cript, as a specification language for JavaScript to
describe JavaScript semantics. We define its abstract syntax, states, and
concrete semantics in the remainder of this section.

@@

\todo
% States $\stset$ consist of heaps $\heapset$ and contexts $\ctxtset$.  A heap
% $\heap \in \heapset$ is a finite mapping from addresses to objects.  Each object
% allocation instruction $x = \kwcl \kwcr$ creates a unique address $\addr \in
% \addrset$ different from existing addresses.  A context $\ctxt \in \ctxtset$ is
% a triple of a label, a environment, and an optional calling context $\ctxtopt
% \in \ctxtoptset = \ctxtset \uplus \{ \bot \}$.  An environment $\env \in
% \envset$ is a finite mapping from variables to values. A value $\val \in
% \valset$ is a primitive value $\pval \in \pvalset$ (e.g., a string value $\str
% \in \strset$), an address $\addr \in \addrset$, a JavaScript AST $\tree \in
% \treeset$, or a function $f \in \funcset$.  A object $\obj \in \objset$ is a
% finite mappings from strings to values.

@@

\subsection{Function Specialization}

@@

A source-to-source transformation is defined with parameteric restrictions
$\restrictset$ and its concretization $\gamma: \restrictset \rightarrow
\powerset{\stset \times \valset^*}$.
\[
  \framebox{$\transf: \funcset \times \restrictset \rightarrow \funcset$}
\]

@@

\subsubsection{Constant Propagation Transformation}
\[
  \begin{array}{lr@{~}c@{~}l}
    \text{Restrictions} & (\valoptset)^* &=& (\valset \uplus \{ \top \})^*\\
    \text{Concretization} & \gamma(\valopt_1, \cdots, \valopt_n) &=& \\
    \multicolumn{4}{l}{\qquad \{
      (\st, (\val_1, \cdots, \val_n)) \mid
      \val_i \in \left\{
        \begin{array}{ll}
          \valset & \text{if} \; \valopt_i = \top\\
          \{ \valopt_i \} & \text{otherwise}\\
        \end{array}
      \right.
    \}}\\
  \end{array}
\]

In the constant propagation transformation, restrictions $(\valoptset)^*$ are
sequences of static values $\valset$ or a dynamic value $\top$.

\[
  \framebox{$\transcpe: \exprset \times \envset \rightarrow \exprset$}
\]

@@

\[
  \framebox{$\transcpi: \instset \times \envset \rightarrow \instset \times
  \envset$}
\]

\[
  \framebox{$\transcpf: \funcset \times (\valoptset)^* \rightarrow \funcset$}
\]

\subsubsection{Redundancy Elimination Transformation}

\[
  \begin{array}{lr@{~}c@{~}l}
    \text{Restrictions} &\{ \top \}\\
    \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
  \end{array}
\]

The redundancy elimination transformation is defined without any restriction,
which means its restriction set consists of a single element $\top$
representing all possible cases.  Therefore, we omit the restriction part in
this transformation for the brevity.

\[
  \framebox{$\transref: \funcset \rightarrow \funcset$}
\]

@@

\subsubsection{Observational Semantics}

@@

\subsection{JavaScript Semantics Specialization}

\subsubsection{Syntatic Views}

\subsubsection{Specialization with Syntatic Views}
